Verification of the CVM algorithm with a Functional Probabilistic Invariant

### 2025-02-26 paper/sec/intro.tex
Edit intro slightly.   - Move line count for neg assoc library to section 6.

We have also mechanized the transformation-based CVM proof by Chakraborty et al.~\cite{chakraborty2022,chakraborty2023}.
As a rough point of comparison, verification of the CVM algorithm using our new technique requires only \locnew~lines in Isabelle/HOL~\cite{nipkow2002}, while the original proof required \locold~lines.

The rest of this paper is organized as follows.
\cref{sec:background} provides background information on randomized algorithms, in particular on their semantics in Isabelle/HOL.
\cref{sec:invariants} introduces our new technique and explains how probabilistic loop invariants can be used to establish tail bounds for the original CVM algorithm.
\cref{sec:negdep} introduces the concept of negative association and our new total and unbiased variant of the CVM algorithm.
\cref{sec:formalization} presents the formalization of both variants of the algorithm, and \cref{sec:formalization_neg_dep} describes our new formalized library on negatively associated random variables.
\cref{sec:transformation_based_proof} discusses some challenges faced in our alternative verification of CVM using the transformation-based proof by Chakraborty et al.
The final sections conclude with an overview of related work and a summary of our results.

>>>>

We carried out the mechanizations using Isabelle/HOL~\cite{nipkow2002}, which comes with a large repository of foundational libraries~\cite{afp} for the verification of randomized algorithms.
We have also mechanized the transformation-based CVM proof by Chakraborty et al.~\cite{chakraborty2022,chakraborty2023}, which provides a rough point of comparison:
Indeed, the verification of the CVM algorithm using our new technique requires only \locnew~lines, while the original proof required \locold~lines.

The rest of this paper is organized as follows.
\cref{sec:background} provides background information on randomized algorithms, in particular on their semantics in Isabelle/HOL.
\cref{sec:invariants} introduces our new technique and explains how probabilistic loop invariants can be used to establish tail bounds for the original CVM algorithm.
\cref{sec:negdep} introduces the concept of negative association and our new total and unbiased variant of the CVM algorithm.
\cref{sec:formalization} presents the formalization of both variants of the algorithm, and \cref{sec:formalization_neg_dep} describes our new formalized library on negatively associated random variables.
\cref{sec:transformation_based_proof} discusses some challenges faced in our alternative verification of CVM using the transformation-based proof by Chakraborty et al.
The final sections present related work and a summary of our results.
